### 2014-11-02 fundamentals/examples.tex
minor revisions

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item the tools in the \Cyclus toolkit
\item and other tools for \Cyclus optimization, parallelization, and development.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosystem.

Already, the ecosystem is growing. Early cross-institutional contributions to 
the ecosystem demonstrate a significant achievement by the \Cyclus framework 
and provide hope for a community-driven development model.

@@

A number of projects and tools outside of the core simulation kernel have been 
developed which improve the scope and the diversity of the capabilities in the \Cyclus 
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
under close integration with the \Cyclus kernel.
\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous Integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools outside of the scope of the \Cyclus kernel have been 
developed for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse 
needs of researchers at various institutions. These archetypes, contributed 
outside of the \Cyclus core and \Cycamore libraries are the first demonstration 
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

@@

Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass MOX recycle is
easy to implement.  The simulation initially included one provider of fresh
UOX fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation duration was set to 1100 months.

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources delineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange makes it easy for a reactor to
preferentially accept recycled MOX fuel over fresh UOX fuel.  The
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\label{fig:flowmodopen}
\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

Simply changing the output commodity name of spent \gls{MOX} fuel from the 
\Class{BatchReactor} transforms this simulation into a closed fuel cycle. Only 
a one-word change in the input file:

@@

This results in new the material flows in Figure \ref{fig:flowclosed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not very realistic for the full, 
multi-pass
recycle case.

\begin{figure}[H]
\label{fig:flowclosed}
\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the scenario described above (all just a single reactor).  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch worth of
fissile material.  Because facilities are represented individually and
transact discrete materials as discrete events, realistic non-uniform patterns
in facility behavior can be observed affecting total system behavior in ways
that are less commonly observed in fleet-based, continuous material flow
modeling.

\begin{figure}[H]
\label{fig:puseries1}
\caption{System plutonium buildup with one reactor.}
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\end{figure}

The open, modified open, and closed scenarios can easily be modified to have
several reactors each with staggered refueling times.  As the number of
reactors increases, the behavior of the system approaches a more steady
average reminiscent of continuous material flow models.  The plutonium buildup
for these three multi-reactor variations is shown in Figure
\ref{fig:puseriesn}.

\begin{figure}[H]
\label{fig:puseriesn}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\end{figure}

>>>>

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven development paradigm. Simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item the tools in the \Cyclus toolkit
\item and other tools for \Cyclus optimization, parallelization, and development.
\end{itemize}
All together, these form an `ecosystem' of capabilities, 
which will grow over time as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosystem.

Already, the ecosystem is growing. Early cross-institutional contributions to 
the ecosystem demonstrate a significant achievement by the \Cyclus framework 
and initiated community-driven development.

@@

A number of projects and tools outside of the core simulation kernel have been 
developed to improve the scope and capabilities of the \Cyclus 
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
under close integration with the \Cyclus kernel.
\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous Integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools outside of the scope of the \Cyclus kernel have been 
developed for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{The range of  archetypes under development reflect the diverse 
needs of researchers at various institutions. These archetypes, contributed 
outside of the \Cyclus core and \Cycamore libraries are the first demonstration 
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

@@

Results of some simple recycle scenarios simulated via \Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass MOX recycle is
easy to implement.  The simulation duration was 1100 months and included one
of each of the following: fresh
UOX fuel fabrication, recycled MOX fuel fabrication, reactor, separations
facility, and repository.

The \Class{BatchReactor} archetype from \Cycamore accepts
fuel materials from an arbitrary number of sources delineated by
commodity. Custom, non-uniform preferences can be set for each fuel
commodity.  The \gls{DRE} enables reactors to
preferentially accept recycled MOX fuel over fresh UOX fuel.  The
\Class{BatchReactor} was configured with a 3-batch core on 18-month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these
simply requires editing input file numbers, as shown below:

@@

The \Class{Source} and \Class{Sink} modules from \Cycamore were chosen to be a
source of fresh, enriched uranium and a repository, respectively. The simple
recycled fuel fabrication facility was designed to
mix fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is similar to
that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in Figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
\label{fig:flowmodopen}
\end{figure}

Simply changing the output commodity name of spent MOX fuel from the 
\Class{BatchReactor} transforms this simulation into a closed fuel cycle.
The one-word change in the input file is shown below:

@@

This new simulation results in the material flows seen in Figure \ref{fig:flowclosed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not accurate for the full, 
multi-pass
recycle case.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the single-reactor scenario described above.  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300) in both the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, the
fabrication facility takes 1 additional cycle to accumulate a full batch of
fissile material.  Because facilities are represented individually and
transact materials as discrete events, realistic non-uniform patterns
in facility behavior can be observed that affect total system behavior in ways
less commonly observed in fleet-based, continuous material flow
modeling.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}

The open, modified open, and closed scenarios can easily be configured to
stagger the refueling times of the reactors.  As the number of
reactors increases, the behavior of the system approaches an average behavior,
reminiscent of continuous material flow models.  The plutonium buildup
for these three multi-reactor variations is shown in Figure
\ref{fig:puseriesn}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\label{fig:puseriesn}
\end{figure}

### 2014-11-02 fundamentals/impl.tex
minor revisions

In addition to the core functionality of the \Cyclus kernel, which is focused on
the minimal set of capabilities needed to implement an agent-based simulation
with dynamic resource exchange, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed module of \Cyclus, with a primary forward-looking
focus on supporting interesting \textit{in situ} (i.e., in simulation) and
\textit{ex situ} (i.e., post-processing) metric analysis tools.

>>>>

In addition to the core functionality of the \Cyclus kernel, which is focused on
the minimal set of capabilities needed to implement an agent-based simulation
with \gls{DRE}, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed module of \Cyclus, with a primary forward-looking
focus on supporting interesting \textit{in situ} (i.e., in simulation) and
\textit{ex situ} (i.e., post-processing) metric analysis tools.

### 2014-11-02 fundamentals/qa.tex
minor revisions

Multiple strategies collectively known as \emph{\gls{QA}} have 
been invented over the years to mitigate the structural and algorithmic errors
on the part of simulators themselves. These include \emph{verification and validation}
(V\&V) \cite{boehm_software_1989}, \emph{uncertainty quantification} (UQ) 
\cite{sacks_design_1989}, testing, and others. V\&V and UQ come from 
a distinctly computational science background while testing \emph{et al.} come from 
a software development bent.

Nuclear enginerering code quality is often governed by NQA-1, an ASME specification 
whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}. This is primarily 
used for designing reactors. However, it is general enough to apply to 
cyclus. Cyclus has adopted an \emph{agile} development process 
\cite{larman_agile_2004}, 
interpreting NQA-1 in a manner similar to NEAMS \cite{neams_nuclear_2013} or 
PyNE \cite{biondo_quality_2014}.

Cyclus acknowledges that quality assurance is an on-going process throughout the 
entire life of the code. As a simulator where most modeling descisions are made 
by third party archetype developers or users, the most important feature of QA 
is verification. Validation may be impossible and UQ is beyond the scope.

Verification may be defined as the question, ``Is cyclus being built correctly?'' 
To answer this question we turn to the software development of notions of testing,
documentation, version control, style guidelines, and continuous integration. 
This suite of process controls supplies mechanims for reliable and reproducible 
software. The impetus to implement these correctly is even stronger in a scientific 
context because of the emphasis on reproducibility and provenance. These are 
discussed below individually.

Validation on the other hand may be defined as the question, 
``Is cyclus the correct tool?''
Since cyclus is alone in its class as an agent-based fuel cycle simulator logitudnal 
validation is not possible. Still code-to-code comparisons with fuel cycle
simulators with other modeling paradigms are underway, if nascent. However, such 
exercises are more likely to bring into relief the differences between the modeling
paradigms than be useful for QA and validation.

@@

It is important to note that before a proposed
code change is allowed into mainline cyclus, all of the tests must pass
and the change must be covered by a test, either new or existing. This is a
matter of policy for the developers. Additionally, test code is equally likely 
as the code it is testing to contain errors. To prevent an infinite recurrsion 
of testing-the-tests, it is assumed that dilligence and one level of testing 
is sufficient to meet the aims of the quality assurance.

@@

Intergration tests are any tests that combine multiple elements of the 
cyclus interface and test that they work correctly with each other.  By analogy, 
simply because the gears (units) are made correctly does not imply that the 
clock (integration) will run smoothly, run at all, or give the correct time.
In cyclus and cycamore, integration tests are performed by running sample
simulations and verifying that results are what would be expected ahead of 
time. Precanned input files have thus been contsructed. Their results 
are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
Python will run cyclus as a subprocess for each integration test. In this
way cyclus code units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that 
major cyclus components are functioning as expected.

@@

Regression tests are tests which ensure that significant changes do not 
occur over the course of cyclus development. Such a change is called a 
\emph{regression} because the new version is almost always wrong version in the 
event of a difference.
Regression tests are implemeneted similarly to integration tests.
Nose is used to execute fully fledged cyclus simulations whose results
are then compared. In this category however the comparison is done against 
the output of the same input file when run with a previous version of cyclus, 
typically the last released version.
In some sense, regression tests are `dumb' in that they do 
not care about the contents of a simulation being correct, only whether or not 
it changed. They thus pick up glaring time-sensitive mistakes that may 
not appear elsewhere though they do not purport to make claims about the
quality of the physics modeled. The cycamore project is the primary location of
regression tests. This is because the archetypes here are sophisticated enough
to make interesting input files. Only a handful ($<10$) time steps are needed 
for regression testing.

@@

All of the public interfaces must be documented as part of cyclus
QA policy. This certifies that the intention for a code unit is communicated 
in way that is separate from its implementation. This policy is important 
because implementations are often wrong. Software implementations are unreliable 
resources about themselves. Truly trustworthy communication about what 
software should be doing comes from the author explicitly stating the 
goals of an API in prose form. Furure development of the code is then able to 
compare the implemetation versus the documentation to discern whether or not they 
are in agreement. Documentation is thus a secondary higher-level information 
source.  In cyclus, this information is aggregated together into static 
websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
\cite{brandl_sphinx_2014} 
tools. These websites are placed online at \url{http://fuelcycle.org}.

@@

Version control is the history-preserving mechanism by which the provenance of 
a code is recored. Cyclus uses a well-established tool called git 
\cite{software_freedom_conservancy_git_2014}
for this purpose. Git is currently the most popular utilty in the recent wave
of \emph{distributed version control}. Briefly stated, this means that every 
user has a complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
Though there and many praises and criticisms of git, one 
feature that the tool performs exceptionally well is the notion of code branches.
These are distinct pathways in the history that branch out of a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
branches may exist at all points in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an 
accompanying message. Thus 
it is possible for cyclus to accurarely replay the entirety of who did what to the
code when.

Cyclus uses a strategy known as \emph{git flow} 
\cite{kalliamvakou_code-centric_2014} 
to manage topical branches where individuals develop code, the mainline development
branch (simply known as develop), and the stable branch (called master).
In addition to these rules and delineation, cyclus also imposes rules on 
when it is accecptable from a quality control standpoint to merge code from 
the personal topical branches into develop. All software at this stage 
must have sufficient and passing tests and reasonable documentation. Without
these core pieces, proposed changes are not allowed into cyclus.

@@

\gls{CI} is the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under \gls{CI} every pull request is tested independently immeadiately after 
it is proposed. Such tests shoudl be run on all officially supported platforms. 
Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.

@@

\gls{CI} has become a neccessary but not sufficient addition to the cyclus QA
system. Its merit is that it keeps bad code out. However, cyclus will always
require human eyes and human hands to let good code in.

>>>>

Multiple strategies collectively known as \emph{\gls{QA}} have 
been invented over the years to mitigate the structural and algorithmic errors
on the part of simulators themselves. These include \emph{\gls{VV}}
\cite{boehm_software_1989}, \emph{\gls{UQ}} 
\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} derive from 
a distinctly computational science background while testing \emph{et al.}
proceed from a software development bent.

Nuclear enginerering code quality is often governed by NQA-1, an ASME specification 
whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}. This is primarily 
used for designing reactors. However, it is general enough to apply to 
\Cyclus. \Cyclus has adopted an \emph{agile} development process 
\cite{larman_agile_2004}, 
interpreting NQA-1 in a manner similar to NEAMS \cite{neams_nuclear_2013} or 
PyNE \cite{biondo_quality_2014}.

\Cyclus acknowledges that quality assurance is an on-going process throughout the 
entire life of the code. As a simulator where most modeling descisions are made 
by third party archetype developers or users, the most important feature of
\gls{QA} 
is verification. Validation may be impossible and \gls{UQ} is beyond the scope.

Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
This question can be answered by the software development of notions of testing,
documentation, version control, style guidelines, and continuous integration. 
This suite of process controls supplies mechanisms for reliable and reproducible 
software. The impetus to implement these correctly is even stronger in a scientific 
context because of the emphasis on reproducibility and provenance. These are 
discussed below individually.

Validation on the other hand may be defined as the question, 
``Is \Cyclus the correct tool?''
Since \Cyclus is alone in its class as an agent-based fuel cycle simulator longitudnal 
validation is not possible. Still code-to-code comparisons with fuel cycle
simulators with other modeling paradigms are underway, if nascent. However, such 
exercises are more likely to bring into relief the differences between the modeling
paradigms than be useful for QA and validation.

@@

It is important to note that before a proposed
code changes is allowed into main stream cyclus, all of the tests must pass
and the change must be covered by a test, either new or existing. This is 
matter of policy for the developers. Additionally, test code is equally likely 
as the code it is testing to contain errors. To prevent an infinite recurrsion 
of testing-the-tests, it is assumed that dilligence and one level of testing 
is sufficient to meet the aims of the quality assurance.

@@

Intergration tests are any tests that combine multiple elemnents of the 
cyclus interface and test that they work correctly with each other.  By analogy, 
simply because the gears (units) are made correctly does not imply that the 
clock (integration) will run smoothly, run at all, or give the correct time.
In cyclus and cycamore, integration tests are performed by running sample
simulations and verifying that results are what would be expected ahead of 
time. Precanned input files have thus been contsructed. Their results 
are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
Python will run cyclus as a subprocess for each integration test. In this
way cyclus code units are tested in the full context that they will
executed. This category of testing is especially useful for ensuring that 
major cyclus components are functioning as expected.

@@

Regression tests are tests which ensure that significant changes do not 
occur over the course of cyclus development. Such a change is called a 
\emph{regression} because the new version is almost always wrong.
Regression tests are implemeneted similarly to integration tests.
Nose is used to execute fully fledged cyclus simulations whose results
are then compared. In this category however the comparison is done against 
the output of the same input file when run with a previous version of cyclus, 
typically the last released version.
In some sense, regression tests are `dumb' in that they do 
not care about the contents of a simulation being correct, only whether or not 
it changed. They thus pick up glaring time-sensitive mistakes that may 
not appear elsewhere though they do not purport to make claims about the
quality of the physics modeled. The cycamore project is the primary location of
regression tests. This is because the archetypes here are sophisticated enough
to make interesting input files. Only a handful ($<10$) time steps are needed 
for regression testing.

@@

All of the public interface (the API) must be documented as part of cyclus
QA policy. This certifies that the intention for a code unit is communicated 
in way that is separate from its implementation. This policy is important 
because implementations are often wrong, hence bugs. They are thus unreliable 
resources about themselves. Truly trustworthy communication about what 
software should be doing comes from the author explicitly stating the 
goals of an API in prose form. Furure development of the code is then able to 
compare the implemetation versus the documentation to discern whether or not they 
are in agreement. Documentation is thus a secondary higher-level information 
stream.  In cyclus, this information is aggregated together into static 
websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
\cite{brandl_sphinx_2014} 
tools. These websites are placed online at \url{http://fuelcycle.org}.

@@

Version control is the history-preserving mechanism by which the provenance of 
a code is recored. Cyclus uses a well-established tool called git 
\cite{software_freedom_conservancy_git_2014}
for this purpose. Git is currently the most popular utilty in the recent wave
of \emph{distributed version control}. Briefly stated, this means that every 
user has a complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
Though there and many praises and criticisms of git, one 
feature that the tool performs exceptionally well is the notion of code branches.
These are distinct pathways in the history that branch out of a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
branches may exist at all point in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an 
accompanying message. Thus 
it is possible for cyclus to accurarely replay the entirety of who did what to the
code when.

Cyclus uses a strategy known as \emph{git flow} 
\cite{kalliamvakou_code-centric_2014} 
to manage topical branches where individuals develop code, the mainline development
branch (simply known as develop), and the stable branch (called master).
In addition to these rules and delineation, cyclus also imposes rules on 
when it is accecptable from a quality control standpoint to merge code from 
the personal topical branches into develop. All software at this stage 
must have sufficient and passing tests and reasonable documentation. Without
these core pieces proposed changes are not allowed into cyclus.

@@

Continuous integration (CI) the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under CI every pull request is tested independently immeadiately after 
it is proposed. Such tests shoudl be run on all officially supported platforms. 
Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.

@@

CI has become a neccessary but not sufficient addition to the cyclus QA
system. Its merit is that it keeps bad code out. However, cyclus will always
require human eyes and human hands to let good code in.
